---
title: "Data report"
author: "University of Cincinnati"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
runtime: shiny
---

## **Chapter #2 : Financial Accounts

**Highlights:**
  On an exchange rate basis, USD is still a stronger currency


## 2.1 Exchange rates
The United States 
``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}

library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
exch_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1551078505&single=true&output=csv"
exch_csv<- read.csv(url(exch_url))
df_exch<- melt(exch_csv, id = "Time")
df_exch$Time <- as.Date(df_exch$Time, format = "%m/%d/%Y")
colnames(df_exch)[1]<- "Year"
colnames(df_exch)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_exch$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_exch
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Exchange rates")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_exch
    data <- spread(mydata1,Country,value)
    data$Year <- as.Date(data$Year, format = "%m/%d/%Y")
    data
  })
}

shinyApp(ui = ui, server = server)
```


## 2.2 Discount rates
The below graph compares discount rates of major economies decided by corresponding central banks
``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
disc_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2051096122&single=true&output=csv"
disc_csv<- read.csv(url(disc_url))
df_disc<- melt(disc_csv, id = "Year")
colnames(df_disc)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_disc$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_disc
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Discount rates")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_disc
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)

```
## 2.3 Inflation - consumer price index
The below graph compares change in consumer price indeces of major economies. The data is converted to annual basis based on average of all months in the year.

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)

infl_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1228243987&single=true&output=csv"
infl_csv <- read.csv(url(infl_url))
df_infl<- melt(infl_csv, id = "Year")
colnames(df_infl)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_infl$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_infl
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Inflation rate")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_infl
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)

```

## **Chapter #3 : Government Policy decisions 


## 3.1 Budget comparison- Surplus or Deficit - major economies 
The below graph ooks into the trend of Budget of USA and other major economies. Positive numbers resemble budget surplus and negative numbers resemble budget deficit.
``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
budg_country_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2079367339&single=true&output=csv"
df_budg <- read.csv(url(budg_country_url))

ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_budg$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_budg
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$Value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Budget (Surplus/Deficit)")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_budg
    data <- spread(mydata1,Country,Value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## 3.2 Debt to GDP ratio - major economies

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
debt_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=353876118&single=true&output=csv"
debt_csv <- read.csv(url(debt_url))
df_debt<- melt(debt_csv, id = "Year")
colnames(df_debt)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_debt$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_debt
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Debt to GDP ratio")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_debt
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## 3.3 Effective tariff rate - manufacturing only
The below graph shows the effective tax rate of manufacturing products as a whole. This compares the major economies wrt to USD. 
``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
tariff_mfg_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1909503509&single=true&output=csv"
tariff_mfg_csv <- read.csv(url(tariff_mfg_url))
df_tariff<- melt(tariff_mfg_csv, id = "Year")
colnames(df_tariff)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_tariff$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_tariff
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Effective tariff rate-Manufacturing")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_tariff
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## 3.4 USA budget - surplus/budget total amount

This graph shows total budget of USA - quantity wise

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
budget_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=956405346&single=true&output=csv"
budget_csv <- read.csv(url(budget_url))
df_budget_usa<- melt(budget_csv, id = "Year")
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE)
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_budget_usa
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("BUdget in total of USA")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_budget_usa
    mydata1
  })
}
shinyApp(ui = ui, server = server)
```

## 3.5 MIllitary percent spend as a percent of GDP - major economies comparison

the below graph shows the comparison of millitary spend as a percent of GDP within all the major economies.

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
millitary_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=353876118&single=true&output=csv"
millitary_csv <- read.csv(url(millitary_url))
df_millitary<- melt(millitary_csv, id = "Year")
colnames(df_millitary)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_millitary$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_millitary
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Millitary spending as a percent GDP ratio")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_millitary
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```