---
title: "Data report_Ch#4- Industrial Indicators"
author: "University of Cincinnati"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
runtime: shiny
---


## Yearly road Vehicles manufactured country wise

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 4.1",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
auto_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2062215672&single=true&output=csv"
auto_csv<- read.csv(url(auto_url))
df_auto<- melt(auto_csv, id = "Year")
df_auto$Year <- as.numeric(df_auto$Year)
colnames(df_auto)[1]<- "Year"
colnames(df_auto)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_auto$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_auto
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Auto production ")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_auto
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## Steel Production in Million metric tons

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 4.2",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
steel_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1173901493&single=true&output=csv"
steel_csv<- read.csv(url(steel_url))
df_steel<- melt(steel_csv, id = "Year")
df_steel$Year <- as.numeric(df_steel$Year)
colnames(df_steel)[1]<- "Year"
colnames(df_steel)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_steel$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_steel
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Million Metric tons")+ggtitle("steel production ")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_steel
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## Aluminium Production in Thousand metric tons

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 4.2",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
alum_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2015095346&single=true&output=csv"
alum_csv<- read.csv(url(alum_url))
df_alum<- melt(alum_csv, id = "Year")
df_alum$Year <- as.numeric(df_alum$Year)
colnames(df_alum)[1]<- "Year"
colnames(df_alum)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_alum$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_alum
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Thousand Metric tons")+ggtitle("Aluminium production ")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_alum
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## Paper & Paperboards Production in Thousand metric tons

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 4.2",message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
paper_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=154072425&single=true&output=csv"
paper_csv<- read.csv(url(paper_url))
df_paper<- melt(paper_csv, id = "Year")
df_paper$Year <- as.numeric(df_paper$Year)
colnames(df_paper)[1]<- "Year"
colnames(df_paper)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_paper$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_paper
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Thousand Metric tons")+ggtitle("paper production ")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_paper
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```


## Job Multipliers : Employment multipliers per $1 million in final demand, by major private-sector industry group
```{r echo=FALSE,results='asis'}
library(knitr)
multiplier_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1946805513&single=true&output=csv"
multiplier_csv<- read.csv(url(multiplier_url))
kable(multiplier_csv,caption= "Job multipliers by sector")
```

## To be added: Mfg labor costs (table)

## Manufacturing as a percentage of GDP
ALREADY uploaded graph in Chapter #1 - as a component of GDPs
