---
title: "Data report"
author: "University of Cincinnati"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
runtime: shiny
---

## **Chapter #6 : Social Indicators

**Highlights:**
Below are the social indicators comparison between countries

## 6.1 Expected years of schooling
``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}

library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
schl_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1191288074&single=true&output=csv"
schl_csv<- read.csv(url(schl_url))
schl_csv$unit
df_schl<- melt(schl_csv, id = "Year")
#df_exch$Year <- as.Date(df_exch$Year, format = "%m/%d/%Y")
colnames(df_schl)[1]<- "Year"
colnames(df_schl)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_schl$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_schl
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Years of Schooling ")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_schl
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```
## 6.2 Public Health expenditure as % of GDP

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}

library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
phealth_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=259706572&single=true&output=csv"
phealth_csv<- read.csv(url(phealth_url))
colnames(phealth_csv)[8] <- "UK"
df_phealth<- melt(phealth_csv, id = "Year")
#df_exch$Year <- as.Date(df_exch$Year, format = "%m/%d/%Y")
colnames(df_phealth)[1]<- "Year"
colnames(df_phealth)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_phealth$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_phealth
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle("Public Health %of GDP")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_phealth
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

## 6.3 Total Health expenditure as % of GDP

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}

library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
health_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=773941787&single=true&output=csv"
health_csv<- read.csv(url(health_url))
df_health<- melt(health_csv, id = "Year")
#df_exch$Year <- as.Date(df_exch$Year, format = "%m/%d/%Y")
colnames(df_health)[1]<- "Year"
colnames(df_health)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_health$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_health
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle(" Health Expenditure %of GDP")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_health
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)

```

## 6.4 Life Expectancy

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}

library(ggplot2)
library(dplyr)
library(reshape)
library(tidyr)
library(shiny)
library(plotly)
library(shinythemes)
lifeexp_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2066172340&single=true&output=csv"
lifeexp_csv<- read.csv(url(lifeexp_url))
df_lifeexp<- melt(lifeexp_csv, id = "Year")
#df_exch$Year <- as.Date(df_exch$Year, format = "%m/%d/%Y")
colnames(df_lifeexp)[1]<- "Year"
colnames(df_lifeexp)[2]<- "Country"
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(df_lifeexp$Country)))
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 = df_lifeexp
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Value")+ggtitle(" Life expectancy")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- df_lifeexp
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```

