---
title: "Data report"
author: "University of Cincinnati"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
runtime: shiny
---
# Introduction




## **Chapter #1 : National Accounts




## 1.1 Output & Growth
 

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.1",message=FALSE}
library(reshape)
library(shiny)
library(plotly)
library(reshape)
library(shinythemes)
library(tidyr)
gdp_url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1100196142&single=true&output=csv"
real_gdp<- read.csv(url(gdp_url))
gdp<- melt(real_gdp,id="Year")
colnames(gdp)[2]<- "Country"
rate_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1116406229&single=true&output=csv"
growth_rate <- read.csv(url(rate_url))
growth_rate<- melt(growth_rate,id="Year")
colnames(growth_rate)[2]<- "Country"
# Define UI for application 
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput(inputId = "data", 
                                                       label = "Topic:",
                                                       choices = c("Total GDP" = "gdp",
                                                                   "Growth rate" = "growth_rate"),
                                                       selected = "Total GDP"),
                                           selectInput("Country", "Country",choices = c("All", levels(gdp$Country))),
                                           sliderInput(inputId = "alpha",label = "Years:",min = 1967,max = 2018,
                                                       value = c(1950, 2019))  
                              ),
                              
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  
  base <- reactive ({get(input$data) })
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata = base()
      mydata1 <- subset(mydata,Year >= input$alpha[1] & Year <= input$alpha[2])
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,
                                          color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab(input$y)+ggtitle(paste("Time series of ",input$data))
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    data <- base()
    data <- spread(data,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```


##  1.2 per capita GDP



``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.2",message=FALSE}
percapita_url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=332948600&single=true&output=csv"
per_capita<- read.csv(url(percapita_url))
percapita<- melt(per_capita,id="Time")
colnames(percapita)[1]<- "Year"
colnames(percapita)[2]<- "Country"
library(shiny)
library(plotly)
library(reshape)
library(shinythemes)
library(tidyr)
# Define UI for application 
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput("Country", "Country",choices = c("All", levels(percapita$Country))),
                                           sliderInput(inputId = "alpha",label = "Years:",min = 1967,max = 2018,
                                                       value = c(1967, 2019))),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata1 <- subset(percapita,Year >= input$alpha[1] & Year <= input$alpha[2])
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country)
      }
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab(input$y)+ggtitle("Time series of Percapita")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- subset(percapita,Year >= input$alpha[1] & Year <= input$alpha[2])
    data <- spread(mydata1,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)

```




##  1.3 Components of GDP (Country wise)

``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.3",message=FALSE}
## consumption as % gdp
consumption_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1052586785&single=true&output=csv"
consumption_gdp <- read.csv(url(consumption_url))
consumption<- melt(consumption_gdp,id="Time")
colnames(consumption)[1]<- "Year"
colnames(consumption)[2]<- "Country"
## manufacturing as  % gdp
mfg_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1438670393&single=true&output=csv"
mfg_gdp<- read.csv(url(mfg_url))
manufacturing<- melt(mfg_gdp,id="Year")
colnames(manufacturing)[2]<- "Country"
## investment as %gdp
investment_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=2075677371&single=true&output=csv"
investment_gdp<- read.csv(url(investment_url))
investment <- melt(investment_gdp, id ="Year")
colnames(investment)[2]<- "Country"
## net exports as % GDP
nx_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1167119739&single=true&output=csv"
nx_gdp <- read.csv(url(nx_url))
net_exports <- melt(nx_gdp, id = "Year")
colnames(net_exports)[1]<- "Year"
colnames(net_exports)[2]<- "Country"
library(reshape)
library(shiny)
library(plotly)
library(reshape)
library(shinythemes)
library(tidyr)
# Define UI for application 
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE),
                                           selectInput(inputId = "data", 
                                                       label = "Topic:",
                                                       choices = c("Manufacturing" = "manufacturing",
                                                                   "Consumption" = "consumption",
                                                                   "Investment"="investment",
                                                                   "Net Exports"="net_exports" ),
                                                       selected = "Manufacturing"),
                                           selectInput("Country", "Country",choices = c("All", levels(consumption$Country))),
                                           sliderInput(inputId = "alpha",label = "Years:",min = 1967,max = 2018,
                                                       value = c(1950, 2019))  
                              ),
                              
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  
  base <- reactive ({get(input$data) })
  output$scatterplot <- renderPlotly({
    ggplotly({
      mydata = base()
      mydata1 <- subset(mydata,Year >= input$alpha[1] & Year <= input$alpha[2])
      if (input$Country != "All") {
        mydata1 <- subset( mydata1,Country == input$Country
        )
      }
      p<- ggplot(data=mydata1, aes_string(x=mydata1$Year, y = mydata1$value,
                                          color = mydata1$Country)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Percentage")+ggtitle(paste("%GDP component: ",input$data))
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    data <- base()
    data <- spread(data,Country,value)
    data
  })
}

shinyApp(ui = ui, server = server)
```



## 1.4 Trade balance 


``````{r fig.width=8, fig.height=4, fig.align='center',echo=FALSE,warning=FALSE,fig.cap = "Figure 1.4.1",message=FALSE}
library(date)
library(reshape)
library(shiny)
library(shinythemes)
## trade balance of USA
trade_url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSFkKmvFq80FC71Qgqys1z8WVyxbxjSQsDWObi86bqcSWheyjU53A0qFfJRxG62HCWO0k1Cv55ed87/pub?gid=1011497714&single=true&output=csv"
trade_gs <- read.csv(url(trade_url))
Trade_balance <- melt(trade_gs, id = "Time")
Trade_balance$Time <- as.Date(Trade_balance$Time, format = "%m/%d/%Y")
colnames(Trade_balance)[1]<- "Year"
colnames(Trade_balance)[2]<- "Type"

# Define UI for application 
ui <- fluidPage(theme = shinytheme("superhero"),
                tabsetPanel(
                  tabPanel( title = "Plot",
                            # Sidebar layout with a input and output definitions
                            sidebarLayout(
                              # Inputs
                              sidebarPanel(numericInput("size", "Point size", 1, 1),
                                           checkboxInput("fit", "Add line of best fit", FALSE)
                              ),
                              # Outputs
                              mainPanel(
                                plotlyOutput(outputId = "scatterplot")
                              )
                            )
                  ),
                  
                  tabPanel(title = "Table",tableOutput("table"))
                )
)

# Define server function required to create the scatterplot
server <- function(input, output) {
  output$scatterplot <- renderPlotly({
    ggplotly({
      
      
      p<- ggplot(data=Trade_balance, aes_string(x=Trade_balance$Year, y = Trade_balance$value,color = Trade_balance$Type)) +
        geom_line(size = input$size) + xlab("Year") + ylab("Trade Balance(Million USD)")+ggtitle("Time series of Trade Balance")
      if (input$fit) {
        p <- p + geom_smooth(method = "lm")
      }
      p
      
    })
  })
  output$table <- renderTable({
    mydata1 <- Trade_balance
    data <- spread(mydata1,Type,value)
    data$Year <- as.Date(data$Year, format = "%m/%d/%Y")
    data
  })
}

shinyApp(ui = ui, server = server)

```



## 1.5 Conclusion
Conclusion for the chapter #1 to be added soon.
